---
title: "User Guide"
author: "Julien Prados, University of Geneva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: bmrm.bib
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
`bmrm` package implements the *Bundle Methods for Regularized Risk Minimization* proposed by @Teo_JMLR_2010 as well as the non-convex extension proposed by @Do_JMLR_2012. This framework is able to solve a minimization problem found in many machine learning algorithm where the goal is to minimze an empirical risk ($R_{emp}(w)$) under a regularization term ($\Omega(w)$):

$$\min_{w} J(w) := \lambda \Omega(w) + R_{emp}(w),$$
where
$$R_{emp} := \frac{1}{m}\sum{l(x_i,y_i,w)}, \lambda > 0$$

The parameter $\lambda$ controls the tradeoff between model fitting and model simplicity and can be tune to precent model overfitting. Different algorithm are obtained by adapting the loss function $l(w,x_i,y_i)$ computed on each training example $(x_i,y_i)$. The package currently implements more than 10 loss functions providing access to powerful algorithms for standand classification and regression, but also for structured prediction: 

| Algorithm                       | Loss Function                        |
|---------------------------------|--------------------------------------|
| linear-SVM                      | `hingeLoss()`                        |
| multiclass-SVM                  | `softMarginVectorLoss()`             |
| max-margin-fbeta-classification | `fbetaLoss()`                        |
| ontology-classification         | `ontologyLoss()`                     |
| epsilon-regression              | `epsilonInsensitiveRegressionLoss()` |
| ordinal-regression              | `ordinalRegressionLoss()`            |
| quantile-regression             | `quantileRegressionLoss()`           |




Furthermore, flexibility of the framework makes it particulary easy to implement custom loss function for all your needs.


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

## References



